Infinite products and zero--one laws in categorical probability

### 2020-05-10 response_to_referees.tex

\renewcommand{\sf}{\mathsf}
\DeclareMathOperator{\del}{del}
\begin{document}
\maketitle

\begin{abstract}
	We would like to thank both referees for their useful suggestions. There are some items that we would like to respond to, in particular from the first referee's report.
\end{abstract}

\section*{Referee 1}

We have been quite surprised by the length and the amount of detail of this report, and it is exciting that the referee has invested so much work into it. The referee's suggestion of putting more emphasis on our infinite tensor products and Kolmogorov products has been helpful for us, and we have shifted the emphasis a bit in that direction.

At the same time, we strongly disagree with the referee on essentially all other counts. In particular, the details below will explain that \textbf{all ``errors'' pointed out in the report are the referee's errors, not ours}. We start by commenting on the summary report and then move on to the material in the attached PDF.

@@

		In fact, the referee already seems to agree with this: the relevant diagram is exactly the referee's one on the second half of p.6 (in the report). The ``new terminology'' that the referee proposes surely does not have any bearing on whether the universal property described by the diagram holds in $\BorelStoch$, right?
\end{enumerate}

On the comments in the PDF:

\begin{enumerate}[resume,label=(\alph*).]
	\item The referee's proposed new formulation of Definition 3.1 is along the lines of our Definition 4.1.\footnote{With the only difference between the preservation by the functors $-\otimes Y$, which we get to in the next item.} In both definitions, the Kolmogorov product is the limit of the finite products $\bigotimes_{i \in F} X_i$ in both $\cC$ and in $\cC_{\det}$. So it is not clear to us what the referee's point is.

		Perhaps the referee's suggestion is to replace Definition 3.1 by Definition 4.1. We do not want to do this, since the latter only applies in Markov categories, while the former more generally makes sense in semicartesian monoidal categories.
		\begin{displayquote}
			and hence every ``infinite tensor product'' is Kolmogorov.
		\end{displayquote}
		This is true in categories like $\Stoch$ and $\BorelStoch$, but not in general. We had already explained this point after Definition 4.1. In conclusion, the distinction between infinite tensor products (in semicartesian monoidal categories, Section 3) and Kolmogorov products (in Markov categories, Section 4) is important and should not be swept under the rug.
	\item Quoting from p.7,
		\begin{displayquote}
			I did not incorporate the property of preservation of lim $\mathcal{D}$ by the endofunctor
			$-\otimes Y : \cC_{\det} \to \cC_{\det}$ because that condition is a global property in the sense
		that $Y$ is an arbitrary element in your space which may have no relationship
		to your fixed family $(X_j)_{j\in J}$ for which you are trying to find an extension.
		\end{displayquote}
		Assuming that ``space'' means category, we agree that there is no relation between $Y$ and the family $(X_i)$, but we do not see why and how this would be an argument against our preservation condition. As the referee will hopefully have noticed, this preservation condition is an important property which we use throughout the paper; in particular, the preservation property is what guarantees the coherence property described in Remark 3.3.

@@

\section*{Referee 2}

We thank the referee for a number of suggestions which have led to an improvement of the presentation. It is good to know for us that the paper is not so easy to follow at times, and we have invested some work into the exposition with the referee's feedback in mind.
